Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-04-07 MainText.Rmd
started writing results for metapopulations

# Introduction\label{intro}

@@

<!--Q2 : metapopulation results : density dependence with extreme tail dep. copula-->

>>>>

# Introduction \label{intro}

@@

<!--Q2 : metapopulation results : density dependence with extreme tail dep. copula-->
We found density-dependence metapopulation models with $n=5$ patches in noisy 
environment showed similar patterns for extinction risk as density-independent 
metapopulation model showed in earlier studies [BIVAN paper]. For each density-dependent 
model listed in Table \ref{tab_model_summary}, we observed higher (or lower) extinction risk for 
the metapopulations when noises across multiple patches were left- (or right) tail dependent.
But that observation remained valid when the model parameter, usually growth rate $(r)$, of each model was 
sufficiently low so that under-compensatory dynamics (monotonous approach towards
its stable equilibrium) for the deterministic analog of the model was ensured. When the model 
was in over-compensatory regime (oscillatory approach towards stable equilibrium) for higher 
value of $r$, we observed right (or left) tail dependent noise caused higher (or lower) extinction 
risk for the metapopulations. All models were consistent with our prediction (see Q2 from \nameref{intro}) 
across local and global dispersal (Figs. \ref{fig_extrisk_allmodel_localdisp} and 
\ref{SM-fig_extrisk_allmodel_globaldisp}).
